Structured Versus Decorated Cospans

### 2020-12-02 cospans.tex
finished going through whole of 2

%%% Christina: the previous formula $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$ doesn't typecheck to me.
%%% Kenny: \phi:1-->F(0), F(!):F(0)-->F(a), F(f):F(a)-->F(a')? Or did I make a mistake somewhere?
%%% Christina: Actually indeed it typechecks, I must have been thinking it does not give me the actual morphism, just one of the two or something. No issue now!

@@

\begin{thm}\label{DC}
Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor. Then the double category $F\lCsp$ is symmetric monoidal, where the tensor product
\begin{itemize}
\item of two objects $a$ and $b$ is their coproduct $a+b$ in $\A$,
\item of two vertical 1-morphisms $f \maps a \to b$ and $f' \maps a' \to b'$ is $f+f' \maps a+a' \to b+b'$ in $\A$,
\item of two horizontal 1-cells $(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$ and $(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ is:
\begin{equation}\label{eq:tensordecoration}
\begin{tikzcd}
& m_1+m_2 & \\
a_1+a_2\ar[ur,"i_1+i_2"] && b_1+b_2,\ar[ul,"o_1+o_2"']
\end{tikzcd}\qquad x_1\oplus x_2:=1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
\end{equation}
%$M_1$ and $M_2$:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$a_1$};
%\node (B) at (1,0) {$m_1$};
%\node (C) at (2,0) {$b_1$};
%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
%\node (E) at (3,0) {$a_2$};
%\node (F) at (4,0) {$m_2$};
%\node (G) at (5,0) {$b_2$};
%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i_1$} (B)
%(C) edge node[above]{$o_1$} (B)
%(E) edge node[above]{$i_2$} (F)
%(G) edge node[above]{$o_2$} (F);
%\end{tikzpicture}
%\]
%is the horizontal 1-cell $M_1 \otimes M_2$:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$a_1+a_2$};
%\node (B) at (1.5,0) {$m_1+m_2$};
%\node (C) at (3,0) {$b_1+b_2$};
%\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i_1+i_2$} (B)
%(C) edge node[above]{$o_1+o_2$} (B);
%\end{tikzpicture}
%\]
%\begin{equation}
%x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
%\end{equation}

\item of two 2-morphisms $\alpha$ and $\beta$ is:
\[
\begin{tikzpicture}[scale=1.2]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
%\node (E) at (2.7,0.5) {$\scriptstyle x \in F(m)$};
\node () at (2.7,0) {$\otimes$};
\node () at (6.2,0) {$=$};
%\node (F) at (2.7,-0.5) {$\scriptstyle x' \in F(m')$};
\node (G) at (3.5,0.5) {$c$};
\node (H) at (4.5,0.5) {$n$};
\node (I) at (5.5,0.5) {$d$};
\node (G') at (3.5,-0.5) {$c'$};
\node (H') at (4.5,-0.5) {$n'$};
\node (I') at (5.5,-0.5) {$d'$};
%\node (J) at (6.7,0.5) {$\scriptstyle y \in F(n)$};
%\node (K) at (6.7,-0.5) {$\scriptstyle y' \in F(n')$};
\node (L) at (1,-1.2) {$\scriptstyle\tau_\alpha \maps F(h)(x) \to x'\textrm{ in } F(m')$};
\node (M) at (4.5,-1.2) {$\scriptstyle\tau_\beta \maps F(h')(y) \to y'\textrm{ in } F(n')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[below] {$i_1'$} (D)
(C') edge node[below] {$o_1'$} (D)
(B) edge node [left] {$h$} (D)
(G) edge node [above] {$i_2$} (H)
(G) edge node [left] {$f'$} (G')
(H) edge node [left] {$h'$} (H')
(G') edge node [below] {$i_2'$} (H')
(I) edge node [above] {$o_2$} (H)
(I) edge node [right] {$g'$} (I')
(I') edge node [below] {$o_2'$} (H');
\end{tikzpicture}
\begin{tikzpicture}[scale=1.1]
\node (A) at (0,0.5) {$a+c$};
\node (A') at (0,-0.5) {$a'+c'$};
\node (B) at (2,0.5) {$m+n$};
\node (C) at (4,0.5) {$b+d$};
\node (C') at (4,-0.5) {$b'+d'$};
\node (D) at (2,-0.5) {$m'+n'$};
%\node (E) at (5.2,0.5) {$\scriptstyle \phi_{m,n}(x,y)$};
%\node (F) at (5.2,-0.5) {$\scriptstyle \phi_{m',n'}(x',y')$};
\node () at (2,-1.3) {$\scriptstyle\tau_{\alpha\ot\beta}\maps F(h+h')(\phi_{m',n'}(x',y'))\to \phi_{m,n}(x,y)\textrm{ in }F(m'+n')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$f+f'$} (A')
(C) edge node[right]{$g+g'$} (C')
(A') edge node [below]{$i_1'+i_2'$} (D)
(C') edge node [below]{$o_1'+o_2'$} (D)
(B) edge node [left] {$h+h'$} (D);
\end{tikzpicture}
\]
with decoration morphism $\tau_{\alpha\otimes\beta}$ given by the following diagram:
\begin{displaymath}
 \begin{tikzcd}[column sep=.5in, row sep=.1in]
& F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] & F(m+n)\ar[dd,"F(h+h')"] \\
1\ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
& F(m')\times F(n')\ar[r,"\phi_{m',n'}"'] & F(m'+n')
 \end{tikzcd}
\end{displaymath}
\end{itemize}
\end{thm}

@@

I_1=\left(0\xrightarrow{!}0\xleftarrow{!}0, 1\xrightarrow{\phi_0}F(0)\right)

@@

a\ar[rr,"i"] && m && b\ar[ll,"o"'] && 1\ar[r,"x"] & F(m)\\

@@

&&1\ar[r,"x\times\phi_0"] & F(m)\times F(0)\ar[r,"\phi_{m,0}"] & F(m+0)

@@

a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &&1\ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)

@@

1\ar[ddrr,dashed,"{(x_1\oplus y_1)\odot(x_2\oplus y_2)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\

@@

1\ar[ddrr,dashed,"{(x_1\odot x_2)\oplus(y_1\odot y_2)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\

@@

Our construction gives not only decorated cospan double categories, but maps betwen these.

@@

\item a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$, 
\item an isomorphism $\theta \maps EF \Rightarrow F'H$:

@@

\node (E) at (0.5,-0.5) {$\Swarrow \theta$};

@@

\item The image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$. In other words, the object component $\lH_0$ of the double functor $\lH$ is the functor $H$.
\item Given a horizontal 1-cell $M$ in $F\lCsp$, which is an $F$-decorated cospan, the image will be the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
\node (D) at (1,-0.5) {$x \in F(m)$};
\node (E) at (2.75,0) {$\mapsto$};
\node (A') at (3.5,0) {$H(a)$};
\node (B') at (4.5,0) {$H(m)$};
\node (C') at (5.5,0) {$H(b)$};
\node (D') at (4.5,-0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
\node (F) at (1,0.5) {$M$};
\node (G) at (4.5,0.5) {$\lH(M)$};
(A') edge node[above]{$H(i)$} (B')
(C') edge node[above]{$H(o)$} (B');
where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite 
\[ 1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
\item Given a 2-morphism $\alpha \colon M \to N$ in $F\lCsp$, which is a map of $F$-decorated cospans, the image will be the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$

@@

\node (G) at (1,-1) {$\tau \maps F(h)(x) \to x'$};

@@

\node (E'') at (8.5,0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
\node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi \in F'(H(n))$};
\node (G'') at (5.75,-1) {$E(\tau) \maps F'(H(h))(\theta_m E(x)\phi) \to (\theta_n E(x')\phi)$};

@@

where given a decoration morphism $\tau \colon F(h)(x) \to x'$, the decoration morphism $E(\tau)$ is defined as:

@@

\node (J) at (-2.5,-0.5) {$\Swarrow \tau$};

@@

@@

@@

\begin{thm}
\label{thm:functoriality}
Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\mathsf{A'}$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F'$} (D);
\end{tikzpicture}
\] 
the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
\end{thm}

>>>>

@@

\begin{thm}\label{DC}
Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor. Then the double category $F\lCsp$ is symmetric monoidal, where the tensor product
\begin{itemize}
\item of two objects $a$ and $b$ is their coproduct $a+b$ in $\A$,
\item of two vertical 1-morphisms $f \maps a \to b$ and $f' \maps a' \to b'$ is $f+f' \maps a+a' \to b+b'$ in $\A$,
\item of two horizontal 1-cells $(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$ and $(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ is:
\begin{equation}\label{eq:tensordecoration}
\begin{tikzcd}
& m_1+m_2 & \\
a_1+a_2\ar[ur,"i_1+i_2"] && b_1+b_2,\ar[ul,"o_1+o_2"']
\end{tikzcd}\qquad x_1\oplus x_2:=\one \xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
\end{equation}
%$M_1$ and $M_2$:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$a_1$};
%\node (B) at (1,0) {$m_1$};
%\node (C) at (2,0) {$b_1$};
%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
%\node (E) at (3,0) {$a_2$};
%\node (F) at (4,0) {$m_2$};
%\node (G) at (5,0) {$b_2$};
%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i_1$} (B)
%(C) edge node[above]{$o_1$} (B)
%(E) edge node[above]{$i_2$} (F)
%(G) edge node[above]{$o_2$} (F);
%\end{tikzpicture}
%\]
%is the horizontal 1-cell $M_1 \otimes M_2$:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$a_1+a_2$};
%\node (B) at (1.5,0) {$m_1+m_2$};
%\node (C) at (3,0) {$b_1+b_2$};
%\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i_1+i_2$} (B)
%(C) edge node[above]{$o_1+o_2$} (B);
%\end{tikzpicture}
%\]
%\begin{equation}
%x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
%\end{equation}

\item of two 2-morphisms $\alpha$ and $\beta$ is:
\[
\begin{tikzpicture}[scale=1.2]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
%\node (E) at (2.7,0.5) {$\scriptstyle x \in F(m)$};
\node () at (2.7,0) {$\otimes$};
\node () at (6.2,0) {$=$};
%\node (F) at (2.7,-0.5) {$\scriptstyle x' \in F(m')$};
\node (G) at (3.5,0.5) {$c$};
\node (H) at (4.5,0.5) {$n$};
\node (I) at (5.5,0.5) {$d$};
\node (G') at (3.5,-0.5) {$c'$};
\node (H') at (4.5,-0.5) {$n'$};
\node (I') at (5.5,-0.5) {$d'$};
%\node (J) at (6.7,0.5) {$\scriptstyle y \in F(n)$};
%\node (K) at (6.7,-0.5) {$\scriptstyle y' \in F(n')$};
\node (L) at (1,-1.2) {$\scriptstyle\tau_\alpha \maps F(h)(x) \to x'\textrm{ in } F(m')$};
\node (M) at (4.5,-1.2) {$\scriptstyle\tau_\beta \maps F(h')(y) \to y'\textrm{ in } F(n')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[below] {$i_1'$} (D)
(C') edge node[below] {$o_1'$} (D)
(B) edge node [left] {$h$} (D)
(G) edge node [above] {$i_2$} (H)
(G) edge node [left] {$f'$} (G')
(H) edge node [left] {$h'$} (H')
(G') edge node [below] {$i_2'$} (H')
(I) edge node [above] {$o_2$} (H)
(I) edge node [right] {$g'$} (I')
(I') edge node [below] {$o_2'$} (H');
\end{tikzpicture}
\begin{tikzpicture}[scale=1.1]
\node (A) at (0,0.5) {$a+c$};
\node (A') at (0,-0.5) {$a'+c'$};
\node (B) at (2,0.5) {$m+n$};
\node (C) at (4,0.5) {$b+d$};
\node (C') at (4,-0.5) {$b'+d'$};
\node (D) at (2,-0.5) {$m'+n'$};
%\node (E) at (5.2,0.5) {$\scriptstyle \phi_{m,n}(x,y)$};
%\node (F) at (5.2,-0.5) {$\scriptstyle \phi_{m',n'}(x',y')$};
\node () at (2,-1.3) {$\scriptstyle\tau_{\alpha\ot\beta}\maps F(h+h')(\phi_{m',n'}(x',y'))\to \phi_{m,n}(x,y)\textrm{ in }F(m'+n')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$f+f'$} (A')
(C) edge node[right]{$g+g'$} (C')
(A') edge node [below]{$i_1'+i_2'$} (D)
(C') edge node [below]{$o_1'+o_2'$} (D)
(B) edge node [left] {$h+h'$} (D);
\end{tikzpicture}
\]
with decoration morphism $\tau_{\alpha\otimes\beta}$ given by the following diagram:
\begin{displaymath}
 \begin{tikzcd}[column sep=.5in, row sep=.1in]
& F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] & F(m+n)\ar[dd,"F(h+h')"] \\
\one \ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
& F(m')\times F(n')\ar[r,"\phi_{m',n'}"'] & F(m'+n')
 \end{tikzcd}
\end{displaymath}
\end{itemize}
\end{thm}

@@

I_1=\left(0\xrightarrow{!}0\xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0)\right)

@@

a\ar[rr,"i"] && m && b\ar[ll,"o"'] && \one \ar[r,"x"] & F(m)\\

@@

&&\one \ar[r,"x\times\phi_0"] & F(m)\times F(0)\ar[r,"\phi_{m,0}"] & F(m+0)

@@

a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &&\one \ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)

@@

\one \ar[ddrr,dashed,"{(x_1\oplus y_1)\odot(x_2\oplus y_2)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\

@@

\one \ar[ddrr,dashed,"{(x_1\odot x_2)\oplus(y_1\odot y_2)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\

@@

Our construction gives not only decorated cospan double categories, but maps betwen these as in \cref{def:doublefun}.

@@

\item a symmetric lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
\item an isomorphism $\theta \maps EF \Rightarrow F'H$: {\chris is this natural or pseudonatural? It should be clarified.}

@@

\node (E) at (0.5,-0.5) {$\Downarrow\theta$};

@@

\item The image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$. 
In other words, the object component $\lH_0$ of the double functor $\lH$ is the functor $H$.
\item The image of an $F$-decorated cospan $M$ in $F\lCsp$ is the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
\begin{align*}
 M=\left(a\xrightarrow{i}m\xleftarrow{o}b,x\in F(m)\right)\mapsto \lH(M)=\left(H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b),\bar{x}\in F'(H(m))\right)& \textrm{ where } \\
\bar{x}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)) &
\end{align*}
%\node (B) at (1,0) {$m$};
%\node (D) at (1,-0.5) {$x \in F(m)$};
%\node (B') at (4.5,0) {$H(m)$};
%\node (D') at (4.5,-0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
%\node (F) at (1,0.5) {$M$};
%\node (G) at (4.5,0.5) {$\lH(M)$};
%where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite 
%\[ 1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
\item The image of a map of decorated cospans $\alpha \colon M \to N$ in $F\lCsp$ is the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$

@@

%\node (G) at (1,-1) {$\tau \maps F(h)(x) \to x'$};

@@

\node (E'') at (8.5,0.5) {$\theta_m E(x) \phi_0 \in F'(H(m))$};
\node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi_0 \in F'(H(n))$};
%\node (G'') at (5.75,-1) {$E(\tau) \maps F'(H(h))(\theta_m E(x)\phi) \to (\theta_n E(x')\phi)$}; %%%Christina: E(tau) is a bad name since it already means something!

@@

where given a decoration morphism $\tau \colon F(h)(x) \to x'$, the induced decoration morphism is:

@@

\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};

@@

\node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(\tau)$};

@@

{\chris There should be an iso on the right if we go with pseudonatural isomorphism}

@@

\begin{thm}
\label{thm:functoriality}
Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\mathsf{A'}$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Downarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F'$} (D);
\end{tikzpicture}
\] 
the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
\end{thm}
